%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames, dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\definecolor{brandeisblue}{rgb}{0.0, 0.44, 1.0}

\usepackage[
	colorlinks=true,
	linkcolor=brandeisblue,
	urlcolor=brandeisblue,
	citecolor=blue,
	anchorcolor=blue
]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{ \vspace{-4pt}\scshape\raggedright\large\bfseries }{}{0em}{}[
\color{black}
\titlerule
\vspace{-5pt}
]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{ \item\small{ {#1 \vspace{-2pt}} } }

\newcommand{\classesList}[4]{ \item\small{ {#1 #2 #3 #4 \vspace{-2pt}} } }

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}
\item
\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
	\textbf{#1}       & \textbf{\small #2} \\
	\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}
\vspace{-8pt}
}

\newcommand{\resumeSubSubheading}[2]{ \item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
	\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}
\vspace{-8pt}
}

\newcommand{\resumeProjectHeading}[2]{ \item
\begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
	\small{#1} & \textbf{\small #2} \\
\end{tabular*}
\vspace{-10pt}
}


\newcommand{\resumeSubItem}[1]{\resumeItem{#1}
\vspace{-6pt}}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\vspace{-6pt}\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}
\vspace{-6pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
	\begin{center}
		{\Huge \scshape Matthew Esposito} \\
		\vspace{1pt}
		Yorktown, VA \\
		\vspace{1pt}
		\href{mailto:maesposito@wm.edu}{\raisebox{-0.2\height}{\faEnvelope}\ \underline{maesposito@wm.edu}}
		~
		\href{https://linkedin.com/in/matthew-esposito-a00813293/}{\raisebox{-0.2\height}{\faLinkedin}\ \underline{linkedin.com/in/matthew-esposito-a00813293}}
        ~
        \href{https://matthew.science/}{\raisebox{-0.2\height}{\faGlobe}\ \underline{matthew.science}}
		\vspace{-8pt}
	\end{center}

	%-----------EDUCATION-----------
	\section{Education}
	\resumeSubHeadingListStart \resumeSubheading {William \& Mary}{Expected May 2026}
	{BS in Computer Science \& BA in Philosophy}{Williamsburg, VA}
	\resumeItemListStart \resumeItem{Lead DevOps, Linux Club; Speaker at W\&M Cypher Hackathon}
	\resumeItem{Awards: 2x W\&M Cypher Hackathon Award, \href{https://nationalcyberleague.org/competition}{Cyber NCL} team placed \textbf{3rd} (Spring `25), \href{https://www.wm.edu/as/computerscience/about-contactus/news/william-mary-cyber-teams-close-out-2024-ranked-6th-in-the-nation.php}{\textbf{6th} (Fall `24)} nationwide}
	\resumeItemListEnd \resumeSubHeadingListEnd

	%------RELEVANT COURSEWORK-------
	\section{Relevant Coursework}
	\begin{multicols}{4}
		{\small \begin{itemize}[itemsep=-5pt, parsep=3pt]\item Algorithms

		\item Computer Organization

		\item Software Development

		\item Finite Automata

		\item Applied Cybersecurity

		\item Cloud Computing

		\item Computer/Network Security

		\item Ethics in Data Science

		\item Philosophy of Technology\end{itemize} }
	\end{multicols}
	\vspace*{2.0\multicolsep}

	%-----------EXPERIENCE-----------
	\section{Experience}
	\resumeSubHeadingListStart

	\resumeSubheading {Memfault}{May 2024 -- August 2024}
	{Software Engineering Intern}{Boston, MA} \resumeItemListStart \resumeItem{Designed and implemented new feature to parse and report stack traces in Rust and Python, }
	\resumeItem{Trained a machine learning model to categorize embedded hardware’s stack traces and core dumps into common fault categories, achieving \>95\% accuracy and helping customers more rapidly fix problems.}
	\resumeItem{Identified and resolved CI/CD bottlenecks, reducing run times and cutting costs.}
	\resumeItem{Created tool to integrate with Algolia APIs to measure engagement in high-potential target accounts.}
	\resumeItemListEnd

	\resumeSubheading {Pex (Remote)}{December 2023 -- April 2024} {Software and Hardware Developer}{}
	\resumeItemListStart \resumeItem{Developed embedded IoT prototypes from inception to testing in 12 weeks}
	\resumeItem{Architected solutions with C++ embedded systems, sound protocols, and cellular modem development}
	\resumeItem{Wrote C++ library for integrating with SIM7600 cellular modem for sub-30ms latency HTTPS/MQTT communication}
	\resumeItemListEnd

	\resumeSubheading {Geospatial Evaluation and Observation Lab}{January 2023 -- Present}
	{Software Developer, Team Lead}{Williamsburg, VA} \resumeItemListStart
	\resumeItem{Built SCOPE, a news info extraction/summarization tool with ML and LLMs.}
	\resumeItem{Led team and developed Kubernetes deployments and CI/CD pipelines.}
	\resumeItemListEnd

	\resumeSubheading {Trilium.cc}{December 2021 -- Present} {Founder}{} \resumeItemListStart
	\resumeItem{Starting a Software-as-a-service business and Linux server management.}
	\resumeItem{Serving over 150 customers and maintaining 99.9\% uptime while learning backend development.}
	\resumeItem{Automated system tasks including backups, updates, and new server deployments with Ansible.}
	\resumeItemListEnd

	\resumeSubHeadingListEnd

	%-----------PROJECTS-----------
	\section{Projects}
	\resumeSubHeadingListStart

	\resumeProjectHeading {\href{https://github.com/redlib-org/redlib}{\textbf{Redlib}} $|$ \emph{Rust, Docker, CI/CD, Reverse Engineering}}{Nov 2022 -- Present}
	\resumeItemListStart \resumeItem{Maintainer of open-source Reddit frontend (2k+ stars, 1M+ container pulls/mo, 100k+ hits/day on popular instances).}
	\resumeItem{Enabled access for censorship-heavy regions, bulk academic research.}
	\resumeItem{Reverse-engineered Reddit mobile API for unthrottled data access.}
	\resumeItem{Implemented peer-to-peer protocol to coordinate handling instance outages live.}
	\resumeItemListEnd

	\resumeProjectHeading {\href{https://focusguardian.org}{\textbf{FocusGuardian}} $|$ \emph{Rust, Vue, C++, PocketBase, Tailwind}}{April 2024}
	\resumeItemListStart \resumeItem{Full-stack web \& mobile app with hardware prototype (C++/LVGL).}
	\resumeItem{Rust-based backend handling DNS-over-HTTPS requests according to user-set schedule, 10k+ req/s.}
	\resumeItem{Built in 24-hour solo hackathon; won Best Hardware Hack.} \resumeItem{Wrote \href{https://matthew.science/posts/focusguardian/}{blog post} about experience.}
	\resumeItemListEnd

	\resumeProjectHeading {\textbf{OccuMetrics} $|$ \emph{C++, IoT, ESP32, Grafana, SQLite, ML}}{Sep 2023 -- Dec 2023}
	\resumeItemListStart \resumeItem{Campus occupancy prediction via IoT devices and serverless stack.}
	\resumeItem{\>90\% accuracy in long-term forecasting using Prophet + time series ML.}
	\resumeItem{\href{https://matthew.science/posts/occupancy/}{Writeup} featured on \href{https://hackaday.com/2023/12/13/bluetooth-as-proxy-for-occupancy/}{Hackaday} and cited in \href{https://efi.mit.edu/spring24/ex01/research}{MIT Engineering courses}.}
	\resumeItemListEnd

	\resumeSubHeadingListEnd

	%-----------RESEARCH-----------
	\section{Research}
	\resumeSubHeadingListStart \resumeSubheading {Vulnerability Testing Report}{Sep 2024 -- Dec 2024}
	{Volunteer Cybersecurity Researcher}{Williamsburg, VA} \resumeItemListStart \resumeItem{Performed a volunteer full security assessment of a local business; authored 22-page CVSS report.}
	\resumeItem{Recommended remediations led to complete patching and mitigation.}
	\resumeItem{Disclosure coordinated; redacted report available on request.}
	\resumeItemListEnd \resumeSubHeadingListEnd

	%-----------LEADERSHIP & COMMUNITY-----------
	\section{Leadership / Community Involvement}
	\resumeSubHeadingListStart

	\resumeSubheading {Linux/FOSS Club}{Sep 2023 -- Present} {Founding Member, DevOps Lead}{Williamsburg, VA}
	\resumeItemListStart \resumeItem{Promoting tech literacy and writing FOSS user guides.}
	\resumeItemListEnd

	\resumeSubheading {Speaker, “A Case for Rust” – W\&M Cypher Hackathon}{March 2023}
	{Sponsored by Rust Foundation}{Williamsburg, VA} \resumeItemListStart
	\resumeItem{Delivered \href{https://matthew.science/rust-talk-matthew-esposito.pdf}{technical talk} and workshop introducing Rust programming.} \resumeItemListEnd

	\resumeSubHeadingListEnd

	%-----------TECHNICAL SKILLS-----------
	\section{Technical Skills}
	\begin{itemize}[leftmargin=0.15in, label={}]
		\small{\item{ \textbf{Technical Areas}{: Backend Development, IoT, Embedded Systems, Systems Programming, DevOps, Docker, Git, Nginx, Prometheus, Grafana} \\ \textbf{Languages}{: Rust, C, C++, C\#, Python, Bash, JavaScript} \\ \textbf{Interests}{: Open Source, Linux, Rust} }}
	\end{itemize}
\end{document}
